All Your Graphs Belong to Us

### 2012-07-19 doc/asplos13/evaluation.tex
more description of trees and performance to uts eval

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves \checkme{81Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node.

Grappa
\TODO{Preston/Simon: why the xmt stops scaling}

>>>>

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism, which both systems depend on.
\todo{data from our trace would be nice here}. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves
\checkme{112Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node. Grappa's scaling slows down at
\checkme{90} machines because of the unscalability of our aggregation
mechanism as there are more network endpoints.

Grappa
\TODO{Preston/Simon: why the xmt stops scaling, readfe retries?}

The XMT plataeus around \checkme{60} processors for 100M, 1.6B, and
4.2B-vertex trees, so performance is not limited by availability of
parallelism for this implementation of UTS-mem.
